Weather Data Integration and Assimilation System\\

### 2020-02-14 lit/sec_1-fews.tex
Moved k8s to architectural decisions

Several weather forecasting, assimilation, and dissemination systems are developed to reduce the damage causing by natural disasters such as flood, storms, hurricanes, and even droughts. %Such natural disasters heavily affected on the economy and the life conditions of the country, researchers have developed systems and many of these systems are using as proprietary systems. 
Other countries are also using those systems while adopting them %with own version of system which effective for the 
to specific weather condition.% in a particular country.
This chapter presents a literature review on existing systems and their architecture approach and design. In \cref{se:fews}, we present \acrshort{fews}. \acrfull{lead}, an open data handling platform distributed as closed-source software, is presented in \cref{se:lead}. % \acrshort{lead} is following the \acrfull{soa} for system architecture. 
In \cref{se:dias}, we discussed about \acrfull{dias} which is a common data platform that can work with weather data. \acrfull{madis} is another widely use data integration system, which also provide data access with quality control, whihc we discuss in \cref{se:madis}.
Under each system we explore both system architecture, scalability, and flexibility of the system.

>>>>

Several weather forecasting, assimilation, and dissemination systems are developed to reduce the damage causing by natural disasters such as flood, storms, hurricanes, and even droughts. %Such natural disasters heavily affected on the economy and the life conditions of the country, researchers have developed systems and many of these systems are using as proprietary systems. 
Other countries are also using those systems while adopting them %with own version of system which effective for the 
to specific weather condition.% in a particular country.
This chapter presents a literature review on existing systems and their architecture approach and design. In \cref{se:fews}, we present \acrshort{fews}. \acrfull{lead}, an open data handling platform distributed as closed-source software, is presented in \cref{se:lead}. % \acrshort{lead} is following the \acrfull{soa} for system architecture. 
In \cref{se:dias}, we discussed about \acrfull{dias} which is a common data platform that can work with weather data. \acrfull{madis} is another widely use data integration system, which also provide data access with quality control, which we discuss in \cref{se:madis}.
Under each system we explore both system architecture, scalability, and flexibility of the system.

### 2020-02-14 lit/sec_3-other-systems.tex
Moved k8s to architectural decisions

\acrshort{dias} collects and files data from satellites, ground observation stations, numerical weather prediction models and climate change projection models. Once this data is integrated with geographic and socio-economic information, DIAS generates results for managing global environmental issues and natural disasters \cite{Kawasaki2018DataReduction}. As mentioned above, \acrshort{dias} has the capability of collecting weather data form multiple data sources which are inherently in different formats. After successfully ingest the data, it generate results which can use for different kind of purposes.

>>>>

\acrfull{dias} collects and files data from satellites, ground observation stations, numerical weather prediction models and climate change projection models. Once this data is integrated with geographic and socio-economic information, DIAS generates results for managing global environmental issues and natural disasters \cite{Kawasaki2018DataReduction}. As mentioned above, \acrshort{dias} has the capability of collecting weather data form multiple data sources which are inherently in different formats. After successfully ingest the data, it generate results which can use for different kind of purposes.

### 2020-02-14 method/sec_0_introduction.tex
Moved k8s to architectural decisions

This chapter includes the design decision taken while implementing the \acrfull{wdias}, and how is the system got adapted from the systems analyzed in Chapter \ref{ch:literature}. %, then how is it trying to propose a better system with overcoming the issues.
In \cref{se:high_level_design} a brief discussion on how the weather forecasting is happening and why it need to interact with multiple data formats is presented. Then following subsections define few termelogy which are using in the \acrshort{wdias}, and scope of the thesis.
\cref{se:architectural_decisions} that we evolve over while designing and implementing the \acrshort{wdias}.
The \cref{se:microservice} gives better understanding of the microservice architectural concepts follows while implementing the \acrshort{wdias}.
Then the reason behind developing Heirarchital Database and technologies use for that discussed in the \cref{se:db_struct}.
Throw out the \cref{se:data_preprocess} discussed about how the \acrshort{wdias} enable for data preprocessing and adding capabilities via concept of Extensions.
Finally, in \cref{se:query} includes details on how to perform timeseries search and geo based queries.

@@

\begin{enumerate}
    \item Extract GRIB WRF model data to netCDF
    \item From netCDF to CSV of each location data, then feed to HEC-HMS and get the output as CSV
    \item CSV and Rain cell Grid feed into the FLO2D, and get the water level as Grid ASCII files after completion of simulation
    \item Upload ASCII files to ArcGIS create Raster files, then use for the LOSS Estimation
\end{enumerate}
When looked into the above flow, it clear understanding on multiple data formats using while weather predictions.
Other than that, to correct the model outputs, it required to collect real time data such as;
\begin{itemize}
    \item Automated weather station sending data in higher frequent intervals via HTTP protocol
    \item Automated water level stations send data in higher frequency
\end{itemize}
Other than above there are many data formats using for handling data based on devices and standards which are using. Also, for data modeling, it needs to convert the data into model compatible data format, then after successfully run the model it needs to collect data from the model output data formats.

@@

dbc{Why are you referring to timeseries here? It's not one of the 3 key components in Fig. 3.1.}
\gkc{Move this to WDIAS microservices \cref{sebse:wdias_microservices}. It need to describe the reason behind decompose into microservices. Seems to be this is confusing at this point.}

>>>>

This chapter includes the design decision taken while implementing the \acrfull{wdias}, and how is the system got adapted from the systems analyzed in Chapter \ref{ch:literature}.
In \cref{se:high_level_design} a brief discussion on how the weather forecasting is happening and why it need to interact with multiple data formats is presented.
\cref{se:architectural_decisions} that we evolve architectural design while designing and implementing the \acrshort{wdias}.
The \cref{se:microservice} gives better understanding of the microservice architectural concepts follows while implementing the \acrshort{wdias}.
Then the reason behind developing Hierarchical Database and technologies use for that discussed in the \cref{se:db_struct}.
Through out the \cref{se:data_preprocess} discussed about how the \acrshort{wdias} enable for data preprocessing and adding capabilities via concept of Extensions.
Final \cref{se:query} includes details on how to perform timeseries search and Geo based queries.

@@

\begin{enumerate}
    \item Extract \acrshort{GRIB} \acrshort{wrf} model data to \acrshort{netCDF}
    \item From \acrshort{netCDF} to \acrshort{csv} of each location data, then feed to HEC-HMS hydro-dynamic model and get the output as \acrshort{csv}
    \item \acrshort{csv} and Rain cell Grid feed into the FLO2D hydro-logic model, and get the water level as ASCII Grid files after completion of simulation
    \item Upload ASCII files to ArcGIS create Raster files, then use for the LOSS Estimation
\end{enumerate}
When looked into the above flow, it clear understanding on multiple data formats using while weather predictions.
Other than that, to correct the model outputs, it required to collect real time data such as;
\begin{itemize}
    \item Automated weather station sending data in higher frequent intervals via HTTP protocol
    \item Automated water level stations send data in higher frequency
\end{itemize}
Other than above there are many data formats using for handling data based on devices and standards which are using. Also, for data modeling, it needs to convert the data into model compatible data format, then after successfully run the model it needs to collect data from the model output data formats.

@@

\dbc{Why are you referring to timeseries here? It's not one of the 3 key components in Fig. 3.1.}
\gkc{Move this to WDIAS microservices \cref{sebse:wdias_microservices}. It need to describe the reason behind decompose into microservices. Seems to be this is confusing at this point.}

### 2020-02-14 method/sec_1-architectural_decisions.tex
Moved k8s to architectural decisions

Initial design of \acrshort{wdias} used the \acrfull{soa}. Moreover, it tried to use an \acrfull{esb} to integrate different modules, as it is acting as a common layer for all of modules. By default, \acrshort{esb} provides publisher/subscribe (pub/sub) capabilities.
\hl{Because} \acrshort{esb} \hl{mediator can be used to integrate the modules which are described in Section} \ref{subse:modules_weather_data_integration_sys}. \acrshort{esb} also support different transportation protocols such as HTTP and Web sockets. However, it turned out that \acrshort{esb} is not a suitable for data streaming or bulk data processing. Also, \acrshort{esb} suffer from single point of failure, as all the messages are going though a common bus.

In the second design round of \acrshort{wdias}, we attempted to use the actor model using AKKA framework \cite{HewittWhyModel}. %However, after consider into the disadvantage of using \acrshort{esb}. 
Using the actors we tried to implement the microservice architecture. In that case, an actor or an actor with slave actors were map to each microservice in \acrshort{wdias}.

/hl{The typical \acrshort{soa} model, for example, usually has more dependent \acrshort{esb}s, with microservices using faster messaging mechanisms. \acrshort{soa} also focuses on imperative programming, whereas microservices architecture focuses on a responsive-actor programming style. Moreover, \acrshort{soa} models tend to have an outsized relational database, while microservices frequently use NoSQL or micro-SQL databases (which can be connected to conventional databases). But the real difference has to do with the architecture methods used to arrive at an integrated set of services in the first place.}
\dbc{Multiple design rounds and decisions are mixed in the para. First finish discussing ESB. Then finish actor model in another para. Then focus on mircoservice details.}

%As mentioned above, \acrshort{esb} support to implement \acrshort{soa}. But \acrshort{soa} has limitations such as single point of failure, slower communication (can’t use for transfer data) etc. So, the microservice architecture get evolved and demanding for the moment. 
When compare to \acrshort{soa}, the microservice architecture has several advantages such as the following:
\begin{itemize}
    \item Follow the Single Responsibility principle
    \item Resilient/flexible as failure in one service does not impact other services. If you have monolithic or bulky service errors in one service/module it can impact other modules/functionality.
    \item High scalable as demanding services can be deployed in multiple servers to enhance performance and keep away from other services so that they do not impact other services. Will be difficult to achieve the same with single, large monolithic service.
    \item Easy to enhance as dependencies are less. Is also easier to change and test.
    \item Low impact on other services as each service is independent. % service., this has less chance to impact other services
    \item Easy to understand since they represent a small piece of functionality
    \item Ease of deployment
\end{itemize}

Even with using the AKKA framework, it has some of the disadvantage as described in AKKA documentation \cite{Akka.ioWhenCluster}. Even Actor model capable of implementing a microservice architecture, it has few disadvantage. To overcome these issues, we moved to the \acrfull{k8s} \cite{LinuxFoundationProduction-GradeKubernetes}.
\dbc{Kubernetes is a product. What you need to refer is to the concept of container-orchestration. Fix.}

\begin{itemize}
    \item \hl{Unable to choose technology. But} \acrshort{k8s} \hl{allows you to choose technology that is best suited for a particular functionality}
    \item \hl{As mentioned in the AKKA documentation} \cite{Akka.ioWhenCluster}, \hl{it is better for developing one microservice within the whole} \acrshort{wdias} design.
\end{itemize}

\dbc{What are these 2 bullets?}
\dbc{Don't use shortened words like it's, isn't, don't,... in writing}

>>>>

Initial design of \acrshort{wdias} used the \acrfull{soa}. Moreover, it tried to use an \acrfull{esb} to integrate different modules, as \acrshort{esb} is acting as a common layer for all of modules. By default, \acrshort{esb} also provides publisher/subscribe (pub/sub) capabilities.
\hl{Because} \acrshort{esb} \hl{mediator can be used to integrate the modules which are described in Section} \ref{subse:modules_weather_data_integration_sys}. 
\gkc{FIXED}
The \acrshort{esb} has the processing units called \emph{mediators}. A mediator can take a message, carry out some predefined actions on it, and output the modified message. This mediator capabilities can use to integrate the modules of a weather data system as shown in \cref{fi:wdia_components}. \acrshort{esb} also support different transportation protocols such as HTTP and Web sockets. However, it turned out that \acrshort{esb} is not a suitable for data streaming or bulk data processing. Also, \acrshort{esb} suffer from single point of failure, as all the messages are going though a common bus and slower communication (can’t use for transfer data).

In the second design phase of \acrshort{wdias}, we attempted to use the actor model using AKKA framework \cite{HewittWhyModel} in order to overcome above \acrshort{esb} drawbacks. At the same time, we moved away from the \acrshort{soa} architecture design to the microservice architecture design. Thus we redesign the system architecture with decompose into microservices and used actors to implement each microservice in the system. In that case, an actor or an actor with slave actors were map to each microservice in \acrshort{wdias}. \acrshort{soa} focuses on imperative programming, whereas microservices architecture focuses on a responsive-actor programming style using faster messaging mechanisms.

When compare to \acrshort{soa}, the microservice architecture has several advantages such as the following:
\begin{itemize}
    \item Follow the Single Responsibility principle
    \item Resilient/flexible as failure in one service does not impact other services. If you have monolithic or bulky service errors in one service/module it can impact other modules/functionality.
    \item High scalable as demanding services can be deployed in multiple servers to enhance performance and keep away from other services so that they do not impact other services. Will be difficult to achieve the same with single, large monolithic service.
    \item Easy to enhance as dependencies are less. Is also easier to change and test.
    \item Low impact on other services as each service is independent. % service., this has less chance to impact other services
    \item Easy to understand since they represent a small piece of functionality
    \item Ease of deployment
\end{itemize}

% /hl{The typical \acrshort{soa} model, for example, usually has more dependent \acrshort{esb}s, with microservices using faster messaging mechanisms. \acrshort{soa} also focuses on imperative programming, whereas microservices architecture focuses on a responsive-actor programming style.}
\dbc{Multiple design rounds and decisions are mixed in the para. First finish discussing ESB. Then finish actor model in another para. Then focus on mircoservice details.}

Even with using the AKKA framework, it has some of the disadvantage with implementing each microservice as an actor as described in AKKA documentation \cite{Akka.ioWhenCluster}. One of the attractive feature of microservice architecture is independent nature of the microservices. This allows to choose a different technology for each microservice based on the advantage that could bring in. Also allowed to independently develop and maintain by multiple smaller and more focused teams/communities. But using the actors as microservice, the actors messaging between different services cause to result in a too tight code coupling between the services and difficulties deploying these independent of each other, which is one of the main reasons for using a microservices architecture \cite{Akka.ioWhenCluster}. To overcome these issues, we moved to the concept of container-orchestration based architecture.

\dbc{Kubernetes is a product. What you need to refer is to the concept of container-orchestration. Fix.}

% \begin{itemize}
%     \item \hl{Unable to choose technology. But} \acrshort{k8s} \hl{allows you to choose technology that is best suited for a particular functionality}
%     \item \hl{As mentioned in the AKKA documentation} \cite{Akka.ioWhenCluster}, \hl{it is better for developing one microservice within the whole} \acrshort{wdias} design.
% \end{itemize}

\dbc{What are these 2 bullets?}
\gkc{Absorbed those two points into above paragraph}
\dbc{Don't use shortened words like it's, isn't, don't,... in writing}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsection{Brief introduction to the \acrfull{k8s}}
% \label{sebse:k8s_intro}

Containerization is an alternative to the virtualization that supports via virtual machines or Hypervisors. It involves encapsulating or packaging up software code and all its dependencies so that it can run uniformly and consistently on any infrastructure \cite{IBMContainerizationExplained}. The concept of containerization and process isolation is emerged after the open source Docker Engine \cite{DockerAppContainerization}, an industry standard for package software into standardized units for development, shipment and deployment.

\acrfull{k8s} is an open-source system for automating deployment, scaling, and management of containerized applications \cite{LinuxFoundationProduction-GradeKubernetes}. It groups containers that make up an application into logical units for easy management and discovery. While implementing the \acrshort{wdias}, we used \acrshort{k8s} as the container-orchestration system, in order to deploy each microservice as container and manage with providing scalability and availability.

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/k8s_architecture_v3.jpg}
    \caption{\acrfull{k8s} architecture.}
    \label{fi:k8s_architecture}
\end{figure}
\cref{fi:k8s_architecture} gives an overall idea on the components of \acrshort{k8s},
\begin{itemize}
    \item Pods -- Cluster of containers that can group other container images in a single unit.
    \item Nodes -- the machines (VMs, physical servers, etc) in a cluster that run your applications and cloud workflows.
    \item kubelet -- An agent that runs on each node in the cluster. It makes sure that containers are running in a pod.
    \item kube-proxy -- A network proxy that runs on each node in the cluster, and maintains network rules on nodes.
    \item Kubernetes master -- Responsible for maintaining the desired state for your cluster.
    \item etcd -- Consistent and highly-available key value store used as Kubernetes’ backing store for all cluster data.
\end{itemize}

Users can add much as required Nodes into the \acrshort{k8s} cluster, and \acrshort{k8s} manage and deploy application as pods into cluster nodes.
Each microservice can deploy as a Pod which is a group of containerize applications. And \acrshort{k8s} able to scale as much as user want as described above.
By separating each microservice as a container, and running them as multiple pods inside the \acrshort{k8s} removes the tight coupling of microservices when compared to the actors. This preserves the independent nature of the microservices which allows to high scale the system.

### 2020-02-14 method/sec_3-microservice.tex
Moved k8s to architectural decisions

\section{Microservice Architecture}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Brief introduction to the \acrfull{k8s}}
\label{sebse:k8s_intro}
\dbc{Don't present this as a separate section. Either this need to be in the literature survey, or integrate key ideas into another section as a paragraph.}

\acrfull{k8s} is an open-source system for automating deployment, scaling, and management of containerized applications \cite{LinuxFoundationProduction-GradeKubernetes}. It groups containers that make up an application into logical units for easy management and discovery.
\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/k8s_architecture_v3.jpg}
    \caption{\acrfull{k8s} architecture.}
    \label{fi:k8s_architecture}
\end{figure}
Components of \acrshort{k8s},
\begin{itemize}
    \item Pods -- Cluster of containers that can group other container images in a single unit.
    \item Nodes -- the machines (VMs, physical servers, etc) in a cluster that run your applications and cloud workflows.
    \item kubelet -- An agent that runs on each node in the cluster. It makes sure that containers are running in a pod.
    \item kube-proxy -- A network proxy that runs on each node in the cluster, and maintains network rules on nodes.
    \item Kubernetes master -- Responsible for maintaining the desired state for your cluster.
    \item etcd -- Consistent and highly-available key value store used as Kubernetes’ backing store for all cluster data.
\end{itemize}
Users can add much as required Nodes into the \acrshort{k8s} cluster, and \acrshort{k8s} manage and deploy application as pods into cluster nodes.
Each microservice can deploy as a Pod which is a group of containerize applications. And \acrshort{k8s} able to scale as much as user want as described above.

>>>>

\section{Microservice Architecture}
\label{se:microservice}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsection{Brief introduction to the \acrfull{k8s}}
% \label{sebse:k8s_intro}
\dbc{Don't present this as a separate section. Either this need to be in the literature survey, or integrate key ideas into another section as a paragraph.}
\gkc{Move this as a paragraph at the end of the architectural design}
